Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation

### 2022-02-15 Manuscript/Tmatrix.tex
modifs pina

\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\usepackage[normalem]{ulem}
\newcommand{\titou}[1]{\textcolor{red}{#1}}
\newcommand{\trashPFL}[1]{\textcolor{red}{\sout{#1}}}
\newcommand{\trashXB}[1]{\textcolor{darkgreen}{\sout{#1}}}
\newcommand{\PFL}[1]{\titou{(\underline{\bf PFL}: #1)}}

@@

The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,vanAggelen_2014,Yang_2014a,Zhang_2015,Zhang_2016,Bannwarth_2020}
\begin{equation}
\label{eq:LR-RPA}
	\begin{pmatrix}
		\bA{}{\ppRPA}			&	\bB{}{\ppRPA}	\\
		-\T{(\bB{}{\ppRPA})}	&	-\bC{}{\ppRPA}	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{n}{N\pm2}	\\
		\bY{n}{N\pm2}	\\
	\end{pmatrix}
	=
	\Om{n}{N\pm2}
	\begin{pmatrix}
		\bX{n}{N\pm2}	\\
		\bY{n}{N\pm2}	\\
	\end{pmatrix}
\end{equation}
where the elements of the various matrices are defined as
\begin{subequations}
\begin{align}
	A_{ab,cd}^{\ppRPA} & = \delta_{ab} \delta_{cd} (\e{a}{} + \e{b}{}) + \mel{ab}{}{cd}
	\\ 
	B_{ab,ij}^{\ppRPA} & = \mel{ab}{}{ij}
	\\ 
	C_{ij,kl}^{\ppRPA} & = - \delta_{ik} \delta_{jl} (\e{i}{} + \e{j}{}) +\mel{ij}{}{kl}
\end{align}
\end{subequations}
and 
\begin{equation}
	\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}
\end{equation}
are two-electron integrals in the spinorbital basis, \ie,
\begin{equation}
	\braket{pq}{rs} = \iint \SO{p}(\bx_1) \SO{q}(\bx_2) \frac{1}{\abs{\br_1 - \br_2}} \SO{r}(\bx_1) \SO{s}(\bx_2)  d\bx_1 d\bx_2
\end{equation}
The pp-RPA problem yields, in the absence of instabilities (which should not appear in Coulombic systems with repulsive interactions only \cite{Scuseria_2013}), $\Nvir(\Nvir-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $\Nocc(\Nocc-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
The pp-RPA correlation energy is given by \cite{Peng_2013,Scuseria_2013}
\begin{equation}
\begin{split}
	\Ec^\ppRPA 
	& = + \sum_n \Om{n}{N+2} - \Tr(\bA{}{\ppRPA}) 
	\\
	& = - \sum_n \Om{n}{N-2} - \Tr(\bC{}{\ppRPA})
\end{split}
\end{equation}

Based on the knowledge of the pp-RPA eigenvalues and eigenvectors, one can then construct the $T$ matrix.
In the spinorbital basis, the correlation part of the $T$ matrix has the following expression \cite{Zhang_2016}
\begin{equation}
\label{eq:T}
	T_{pq,rs}(\omega) 
		= \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + i\eta}
		- \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega - \Om{n}{N-2} - i\eta}
\end{equation}
with
\begin{subequations}
\begin{align}
	\braket*{pq}{\chi_n^{N+2}} & = \sum_{c < d} \mel{pq}{}{cd} X_{cd,n}^{N+2} + \sum_{k < l}  \mel{pq}{}{kl} Y_{kl,n}^{N+2}
	\\
	\braket*{pq}{\chi_n^{N-2}} & = \sum_{c < d} \mel{pq}{}{cd} X_{cd,n}^{N-2} + \sum_{k < l}  \mel{pq}{}{kl} X_{kl,n}^{N-2}
\end{align}
\end{subequations}

Combining Eqs.~\eqref{eq:G} and \eqref{eq:T}, the correlation part of the $T$-matrix self-energy reads \cite{Romaniello_2012,Martin_2016,Zhang_2017,Li_2021b}
\begin{equation}
\label{eq:SigGT}
	\Sigma^{GT}_{pq}(\omega)
	= \sum_{in} \frac{\braket*{pi}{\chi_n^{N+2}}\braket*{qi}{\chi_n^{N+2}}}{\omega + \e{i}{} - \Om{n}{N+2} + i\eta}
	- \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2} - i\eta}
\end{equation}
While the dynamical $GW$ self-energy corresponds to the downfolding of the 2h1p and 2p1h configurations on the 1h and 1p configurations via their coupling with the 1h1p configurations, respectively, \cite{Bintrim_2021a} Eq.~\eqref{eq:SigGT} shows that, in the case of the $T$-matrix approximation, the same 2h1p and 2p1h configurations are downfolded on the 1p and 1h configurations via their coupling with the 2h and 2p configurations, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Neutral excitations}
\label{sec:neutral}
%%%%%%%%%%%%%%%%%%%%%%
Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE 
\begin{multline}
	 iL(1,2;1',2') = L_0(1,2;1',2') 
	 \\
	 + \int L_0(1,4;1',3) \Xi(3,5;4,6) L(6,2;5,2') d3d4d5d6
\end{multline}
where
\begin{subequations}
\begin{align}
\label{eq:L0}
	 iL_0(1,4;1',3) & = G(1,3) G(4,1')
	 \\
\label{eq:L}
	 iL(1,2;1',2') & = -G_2(1,2;1',2') + G(1,1')G(2,2')
\end{align}
\end{subequations}
and 
\begin{equation}
\label{eq:Xi}
	\Xi(3,5;4,6) = i \fdv{\Sigma(3,4)}{G(6,5)}
\end{equation}
is the so-called BSE kernel that takes into account the self-consistent variation of $\Sigma$ with respect to the variation of $G$.
By taking into account the interaction of the excited electron and its hole left behind (the infamous excitonic effect), the BSE is able to faithfully model (neutral) optical excitations as measured by absorption spectroscopy. 
The moderate cost of the BSE [which scales as $\order*{K^4}$ in its standard implementation] and its all-round accuracy are the main reasons behind its growing popularity in the molecular electronic structure community. \cite{Rohlfing_1999a,Horst_1999,Puschnig_2002,Tiago_2003,Boulanger_2014,Jacquemin_2015a,Bruneval_2015,Jacquemin_2015b,Hirose_2015,Jacquemin_2017a,Jacquemin_2017b,Rangel_2017,Krause_2017,Gui_2018,Blase_2018,Liu_2020,Blase_2020,Holzer_2018a,Holzer_2018b,Loos_2020e,Loos_2021}

@@

Due to the frequency-independent nature of the static BSE, it is well known that one cannot access double (and higher) excitations.
\cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
In order to go beyond the static approximation, it is possible to consider, within the dynamical TDA (dTDA) that neglects the frequency dependence of the coupling block $\bB{}{}$, the dynamical version of the BSE (dBSE). \cite{Strinati_1988,Romaniello_2009b,Loos_2020h}
In this case, one must solve the (non-linear) dynamical eigenvalue problem
\begin{equation}
\label{eq:dBSE}
	\begin{pmatrix}
		\bA{}{\dBSE}(\Om{S}{})	&	\bB{}{\BSE}	\\
		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\Om{S}{})	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
	=
	\Om{S}{}
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
\end{equation}
with 
\begin{equation}
	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega)
\end{equation}
where, following Strinati's seminal work, \cite{Strinati_1988} one can derive the following expression for the elements of the dynamical $T$ matrix
\begin{equation}
\label{eq:dT}
\begin{split}
	\widetilde{T}_{pq,rs}(\omega) 
		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\e{i}{\GT} + \e{j}{\GT}) + i\eta}
		\\
		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\e{a}{\GT} + \e{b}{\GT}) + i\eta}
\end{split}
\end{equation}
from which, one can check that we recover the static expression \eqref{eq:T} in the limit $\Om{n}{N\pm2} \to \infty$.
Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, \cite{Strinati_1988,Romaniello_2009b,Loos_2020h} the 2h2p configurations are downfolded on the 1h1p configurations. \cite{Bintrim_2021b}
Additional details about the derivation of Eq.~\eqref{eq:dT} are reported in Appendix \ref{app:dBSE}.

@@

Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except maybe for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
Moreover, triplet instabilities seems to affect BSE@$G_0T_0$ slightly earlier than BSE@$G_0W_0$.

@@

In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE  amplitude
\begin{equation}
\label{eq:Strinati_1}
	\chi_S(1,1') = \int d3d4d5d6L_0(1,4,1',3)\Xi(3,5,4,6) \chi_S(6,5)
\end{equation}
where $L_0$ is given by Eq.~\eqref{eq:L0} and the $T$-matrix kernel is
\begin{equation}
\label{eq:T-matrix_kernel}
	\Xi(3,5,4,6) =  i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6)
\end{equation}
Equation (\ref{eq:Strinati_1}) is derived by assuming that i) the (resonant) pole $\omega_S=E_S-E_0>0$ of $L$ is isolated from the other poles (which is usually the case for neutral excitations in finite systems), and  ii) the poles of $L_0$ are different form $\omega_S$ (which is also generally the case).
The so-called $T$-matrix self-energy $\Sigma$ is given by Eq.~\eqref{eq:SigGT} with \cite{Martin_2016,Romaniello_2012}
\begin{equation}
\label{eq:T-matrix}
	T(3,8,4,7) =
	- v(3,8)\delta(3,4)\delta(7,8)
	+ v(3,8)\delta(4,8)\delta(3,7)
	+ i \int d1'd2' v(3,8)G(3,1')G(8,2')T(1',2',4,7)
\end{equation}  
where $v$ is the bare Coulomb operator and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$. 
The first two terms in the right-hand side of Eq.~\eqref{eq:T-matrix} are the Hartree and exchange contributions to the $T$-matrix, whereas the last term is the correlation contribution.
Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit and defining $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$, one gets 
\begin{equation}
\label{eq:DYN_T}
	\chi_S(\bx_1,\bx_{1'},\tau_{11'})e^{-i\omega_S(t_1+t_{1'})/2}
	=-i\int d3d4d5d6 G(\bx_1,\bx_3;\tau_{13})G(\bx_4,\bx_{1'};\tau_{11'})
	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
\end{equation}
[where $\tau_{ij}=t_i-t_j$ and $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$)] and
\begin{multline}
\label{eq:T_bar}
	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) 
	= v(\bx_3,\bx_5)\delta(\tau_{34})\delta(\bx_3,\bx_4)\delta(\bx_6,\bx_5)-v(\bx_3,\bx_5)\delta(\tau_{34})	\delta(\bx_3,\bx_6)\delta(\bx_4,\bx_5)
	\\
	+ i \int d7 d8 v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{38})G(\bx_5,\bx_8;\tau^+_{38})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{84})
\end{multline}
Using the Fourier transform $G(\tau)=\int \frac{d\omega}{2\pi}G(\omega)e^{-i\omega\tau}$, changing variable from $t_3$ to $\tau_{34}$ and taking the limit $t_{1'}=t_1^+$, we have
\begin{multline}
	\chi_S(\bx_1,\bx_{1'},0^-)
	= -i\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int d\tau_{34} \int \frac{d\omega'}{2\pi}G(\bx_1,\bx_3;\omega'+\omega_S)G(\bx_4,\bx_{1'};\omega')e^{i\omega'\tau_{34}}
	\\
	 \times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
\end{multline}
Using the Lehman representation of the one-body Green's function in the quasiparticle approximation given by Eq.~\eqref{eq:G}, and multiply the left- and right-hand sides by $(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1 d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')$, we obtain  
\begin{multline}
\label{eq:General_DYN}
	\qty(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')  \chi_S(\bx_1,\bx_{1'},0^-) =
	-\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int d\tau_{34}\SO{a}(\bx_3)\SO{i}(\bx_4)
	\\
	\times \qty[\Theta(\tau_{34})e^{i\e{i}{}\tau_{34}}+\Theta(-\tau_{34})e^{i(\e{a}{}-\omega_S)\tau_{34}} ]
	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
\end{multline}
(where $\Theta$ is the Heaviside step function) using the fact that
\begin{equation}
	\Theta(\pm\tau)e^{-i\alpha \tau}=\mp\frac{1}{2\pi i}\lim_{\eta\to 0^+}\int d\omega \frac{1}{\omega-\alpha\pm i\eta}e^{-i\omega\tau}
\end{equation}

>>>>

\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}
\newcommand{\alert}[1]{\textcolor{red}{#1}}
\usepackage[normalem]{ulem}
\newcommand{\pina}[1]{\textcolor{blue}{#1}}
\newcommand{\titou}[1]{\textcolor{red}{#1}}
\newcommand{\trashPFL}[1]{\textcolor{red}{\sout{#1}}}
\newcommand{\trashXB}[1]{\textcolor{darkgreen}{\sout{#1}}}
\newcommand{\PFL}[1]{\titou{(\underline{\bf PFL}: #1)}}

@@

The non-Hermitian pp-RPA problem reads \cite{Schuck_Book,vanAggelen_2013,Peng_2013,Scuseria_2013,Yang_2013,Yang_2013b,vanAggelen_2014,Yang_2014a,Zhang_2015,Zhang_2016,Bannwarth_2020}
\begin{equation}
\label{eq:LR-RPA}
	\begin{pmatrix}
		\bA{}{\ppRPA}			&	\bB{}{\ppRPA}	\\
		-\T{(\bB{}{\ppRPA})}	&	-\bC{}{\ppRPA}	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{n}{N\pm2}	\\
		\bY{n}{N\pm2}	\\
	\end{pmatrix}
	=
	\Om{n}{N\pm2}
	\begin{pmatrix}
		\bX{n}{N\pm2}	\\
		\bY{n}{N\pm2}	\\
	\end{pmatrix}
\end{equation}
where the elements of the various matrices are defined as
\begin{subequations}
\begin{align}
	A_{ab,cd}^{\ppRPA} & = \delta_{ab} \delta_{cd} (\e{a}{} + \e{b}{}) + \mel{ab}{}{cd}
	\\ 
	B_{ab,ij}^{\ppRPA} & = \mel{ab}{}{ij}
	\\ 
	C_{ij,kl}^{\ppRPA} & = - \delta_{ik} \delta_{jl} (\e{i}{} + \e{j}{}) +\mel{ij}{}{kl}
\end{align}
\end{subequations}
and 
\begin{equation}
	\mel{pq}{}{rs} = \braket{pq}{rs} - \braket{pq}{sr}
\end{equation}
are two-electron integrals in the spinorbital basis, \ie,
\begin{equation}
	\braket{pq}{rs} = \iint \SO{p}(\bx_1) \SO{q}(\bx_2) \frac{1}{\abs{\br_1 - \br_2}} \SO{r}(\bx_1) \SO{s}(\bx_2)  d\bx_1 d\bx_2
\end{equation}
The pp-RPA problem yields, in the absence of instabilities (which should not appear in Coulombic systems with repulsive interactions only \cite{Scuseria_2013}), $\Nvir(\Nvir-1)/2$ positive eigenvalues $\Om{n}{N+2}$ and $\Nocc(\Nocc-1)/2$ negative eigenvalues $\Om{n}{N-2}$, which  correspond respectively to double attachments and double detachments.
The pp-RPA correlation energy is given by \pina{Is this important? We don't calculate the correlation energy} \cite{Peng_2013,Scuseria_2013}
\begin{equation}
\begin{split}
	\Ec^\ppRPA 
	& = + \sum_n \Om{n}{N+2} - \Tr(\bA{}{\ppRPA}) 
	\\
	& = - \sum_n \Om{n}{N-2} - \Tr(\bC{}{\ppRPA})
\end{split}
\end{equation}

Based on the knowledge of the pp-RPA eigenvalues and eigenvectors, one can then construct the $T$ matrix.
In the spinorbital basis, the correlation part of the $T$ matrix has the following expression\pina{We have to be careful with the notation, because the relation between this T and the T in the appendix is a minus sign. See also supporting information Eqs 0.23-0.24} \cite{Zhang_2016}
\begin{equation}
\label{eq:T}
	T_{pq,rs}(\omega) 
		= \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + i\eta}
		- \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega - \Om{n}{N-2} - i\eta}
\end{equation}
with
\begin{subequations}
\begin{align}
	\braket*{pq}{\chi_n^{N+2}} & = \sum_{c < d} \mel{pq}{}{cd} X_{cd,n}^{N+2} + \sum_{k < l}  \mel{pq}{}{kl} Y_{kl,n}^{N+2}
	\\
	\braket*{pq}{\chi_n^{N-2}} & = \sum_{c < d} \mel{pq}{}{cd} X_{cd,n}^{N-2} + \sum_{k < l}  \mel{pq}{}{kl} X_{kl,n}^{N-2}
\end{align}
\end{subequations}

Combining Eqs.~\eqref{eq:G} and \eqref{eq:T}, the correlation part of the $T$-matrix self-energy reads \cite{Romaniello_2012,Martin_2016,Zhang_2017,Li_2021b}
\begin{equation}
\label{eq:SigGT}
	\Sigma^{GT}_{pq}(\omega)
	= \sum_{in} \frac{\braket*{pi}{\chi_n^{N+2}}\braket*{qi}{\chi_n^{N+2}}}{\omega + \e{i}{} - \Om{n}{N+2} + i\eta}
	+ \sum_{an} \frac{\braket*{pa}{\chi_n^{N-2}}\braket*{qa}{\chi_n^{N-2}}}{\omega + \e{a}{} - \Om{n}{N-2} - i\eta}
\end{equation}
While the dynamical $GW$ self-energy corresponds to the downfolding of the 2h1p and 2p1h configurations on the 1h and 1p configurations via their coupling with the 1h1p configurations, respectively, \cite{Bintrim_2021a} Eq.~\eqref{eq:SigGT} shows that, in the case of the $T$-matrix approximation, the same 2h1p and 2p1h configurations are downfolded on the 1p and 1h configurations via their coupling with the 2h and 2p configurations, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%
\section{Neutral excitations}
\label{sec:neutral}
%%%%%%%%%%%%%%%%%%%%%%
Like the one-body Green's function is the pillar of the $GW$ and $GT$ approximations, the two-body Green's function $G_2$ is the central quantity of the Bethe-Salpeter equation (BSE) formalism of many-body perturbation theory \cite{Salpeter_1951,Strinati_1988,Blase_2018,Blase_2020} via its link with the two-body correlation function $L$ which satisfies the self-consistent BSE \pina{what do u mean? BSE as a Dyson equation? Maybe like this it seems that we solve self-consistently the BSE, which is not the case} 
\begin{multline}
	 \pina{i}L(1,2;1',2') = L_0(1,2;1',2') 
	 \\
	 + \int L_0(1,4;1',3) \Xi(3,5;4,6) L(6,2;5,2') d3d4d5d6
\end{multline}
where
\begin{subequations}
\begin{align}
\label{eq:L0}
	 iL_0(1,4;1',3) & = G(1,3) G(4,1')
	 \\
\label{eq:L}
	 iL(1,2;1',2') & = -G_2(1,2;1',2') + G(1,1')G(2,2')
\end{align}
\end{subequations}
and 
\begin{equation}
\label{eq:Xi}
	\Xi(3,5;4,6) = i \fdv{\Sigma(3,4)}{G(6,5)}
\end{equation}
is the so-called BSE kernel that takes into account the self-consistent variation \pina{what do u mean?} of $\Sigma$ with respect to the variation of $G$.
By taking into account the interaction of the excited electron and its hole left behind (the infamous excitonic effect), the BSE is able to faithfully model (neutral) optical excitations as measured by absorption spectroscopy. 
The moderate cost of the BSE [which scales as $\order*{K^4}$ in its standard implementation] and its all-round accuracy are the main reasons behind its growing popularity in the molecular electronic structure community. \cite{Rohlfing_1999a,Horst_1999,Puschnig_2002,Tiago_2003,Boulanger_2014,Jacquemin_2015a,Bruneval_2015,Jacquemin_2015b,Hirose_2015,Jacquemin_2017a,Jacquemin_2017b,Rangel_2017,Krause_2017,Gui_2018,Blase_2018,Liu_2020,Blase_2020,Holzer_2018a,Holzer_2018b,Loos_2020e,Loos_2021}

@@

Due to the frequency-independent nature of the static BSE, it is well known that one cannot access double (and higher) excitations.
\cite{Loos_2019,Romaniello_2009b,Sangalli_2011,Loos_2020h,Authier_2020,Monino_2021}
In order to go beyond the static approximation, it is possible to consider, within the dynamical TDA (dTDA) that neglects the frequency dependence of the coupling block $\bB{}{}$, the dynamical version of the BSE (dBSE). \cite{Strinati_1988,Romaniello_2009b,Loos_2020h}
In this case, one must solve the (non-linear) dynamical eigenvalue problem
\begin{equation}
\label{eq:dBSE}
	\begin{pmatrix}
		\bA{}{\dBSE}(\Om{S}{})	&	\bB{}{\BSE}	\\
		-\bB{}{\BSE}	&	-\bA{}{\dBSE}(-\Om{S}{})	\\
	\end{pmatrix}
	\cdot
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
	=
	\Om{S}{}
	\begin{pmatrix}
		\bX{S}{\dBSE}	\\
		\bY{S}{\dBSE}	\\
	\end{pmatrix}
\end{equation}
with 
\begin{equation}
	A_{ia,jb}^{\dBSE}(\omega) = \delta_{ij} \delta_{ab} (\e{a}{\GT} - \e{i}{\GT}) + \mel{ib}{}{aj} - \widetilde{T}_{ib,aj}(\omega)
\end{equation}
where, following Strinati's seminal work, \cite{Strinati_1988} one can derive the following expression for the elements of the dynamical $T$ matrix
\begin{equation}
\label{eq:dT}
\begin{split}
	\widetilde{T}_{pq,rs}(\omega) 
		& = \sum_{n} \frac{\braket*{pq}{\chi_n^{N+2}}\braket*{rs}{\chi_n^{N+2}}}{\omega - \Om{n}{N+2} + (\pina{\e{i}{\GT}} + \pina{\e{j}{\GT}}) + i\eta}
		\\
		& + \sum_{n} \frac{\braket*{pq}{\chi_n^{N-2}}\braket*{rs}{\chi_n^{N-2}}}{\omega + \Om{n}{N-2} - (\pina{\e{a}{\GT}} + \pina{\e{b}{\GT}}) + i\eta}
\end{split}
\end{equation}
from which, one can check that we recover the static expression \eqref{eq:T} in the limit $\Om{n}{N\pm2} \to \infty$.
Equation \eqref{eq:dT} highlights the interesting dynamical structure of the $T$ matrix, where, similarly to the dBSE@$GW$ scheme, \cite{Strinati_1988,Romaniello_2009b,Loos_2020h} the 2h2p configurations are downfolded on the 1h1p configurations. \cite{Bintrim_2021b}
Additional details about the derivation of Eq.~\eqref{eq:dT} are reported in Appendix \ref{app:dBSE}.

@@

Similar observations can be made for the triplet states, the $GW$- and $GT$-based formalisms yielding very similar excitation energies, except \pina{maybe} for the $\text{c}\,{}^3\Pi_u$ state for which BSE@$G_0W_0$ has clearly the edge.
Moreover, triplet instabilities seems to affect BSE@$G_0T_0$ slightly earlier than BSE@$G_0W_0$.

@@

In order to derive the dynamical kernel $\tilde{T}_{ib,aj}$ given in Eq.~\eqref{eq:dT}, we follow Ref.~\onlinecite{Strinati_1980} (see also Ref.~\onlinecite{Loos_2020e}) and start from the equation for the BSE  amplitude
\begin{equation}
\label{eq:Strinati_1}
	\chi_S(1,1') = \int d3d4d5d6L_0(1,4,1',3)\Xi(3,5,4,6) \chi_S(6,5)
\end{equation}
where $L_0$ is given by Eq.~\eqref{eq:L0} and the $T$-matrix kernel is
\begin{equation}
\label{eq:T-matrix_kernel}
	\Xi(3,5,4,6) =  i\frac{\delta \Sigma(3,4)}{\delta G(6,5)}\approx -T(3,5,4,6)
\end{equation}
Equation (\ref{eq:Strinati_1}) is derived by assuming that i) the (resonant) pole $\omega_S=E_S-E_0>0$ of $L$ is isolated from the other poles (which is usually the case for neutral excitations in finite systems), and  ii) the poles of $L_0$ are different form $\omega_S$ (which is also generally the case).
The so-called $T$-matrix self-energy $\Sigma$ is given by Eq.~\eqref{eq:SigGT} with \cite{Martin_2016,Romaniello_2012}
\begin{equation}
\label{eq:T-matrix}
	T(3,8,4,7) =
	- v(3,8)\delta(3,4)\delta(7,8)
	+ v(3,8)\delta(4,8)\delta(3,7)
	+ i \int d1'd2' v(3,8)G(3,1')G(8,2')T(1',2',4,7)
\end{equation}  
where $v$ is the bare Coulomb operator and we neglect the functional derivative $\delta T/\delta G$ in the kernel $\Xi$. 
The first two terms in the right-hand side of Eq.~\eqref{eq:T-matrix} are the Hartree and exchange contributions to the $T$-matrix, whereas the last term is the correlation contribution.
Making the time dependence of Eq.~\eqref{eq:Strinati_1} explicit and defining $T(3,5,4,6)=- \delta(\tau^+_{35})\delta(\tau^+_{64})\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})$, one gets 
\begin{equation}
\label{eq:DYN_T}
	\chi_S(\bx_1,\bx_{1'},\tau_{11'})e^{-i\omega_S(t_1+t_{1'})/2}
	=-i\int d\bx_3d\bx_4d\bx_5d\bx_6\int dt_3dt_4 G(\bx_1,\bx_3;\tau_{13})G(\bx_4,\bx_{1'};\tau_{11'})
	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
\end{equation}
[where $\tau_{ij}=t_i-t_j$ and $\tau^+_{ij}=t^+_i-t_j$ with $t^+_i=t_i+\eta$ ($\eta \to 0^+$)] and
\begin{multline}
\label{eq:T_bar}
	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34}) 
	= v(\bx_3,\bx_5)\delta(\tau_{34})\delta(\bx_3,\bx_4)\delta(\bx_6,\bx_5)-v(\bx_3,\bx_5)\delta(\tau_{34})	\delta(\bx_3,\bx_6)\delta(\bx_4,\bx_5)
	\\
	+ i \int d\bx_7 d\bx_8\int t_ v(\bx_3,\bx_5)G(\bx_3,\bx_7;\tau_{37})G(\bx_5,\bx_8;\tau^+_{37})\Bar{T}(\bx_7,\bx_8,\bx_4,\bx_6;\tau_{74})
\end{multline}
Using the Fourier transform $G(\tau)=\int \frac{d\omega}{2\pi}G(\omega)e^{-i\omega\tau}$, changing variable from $t_3$ to $\tau_{34}$ and taking the limit $t_{1'}=t_1^+$, we have
\begin{multline}
	\chi_S(\bx_1,\bx_{1'},0^-)
	= -i\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int d\tau_{34} \int \frac{d\omega'}{2\pi}G(\bx_1,\bx_3;\omega'+\omega_S)G(\bx_4,\bx_{1'};\omega')e^{i\omega'\tau_{34}}
	\\
	 \times \Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{-i\omega_S\tau_{34}/2}
\end{multline}
Using the Lehman representation of the one-body Green's function in the quasiparticle approximation given by Eq.~\eqref{eq:G}, and multiply the left- and right-hand sides by $(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1 d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')$, we obtain  
\begin{multline}
\label{eq:General_DYN}
	\qty(\e{a}{}-\e{i}{}-\omega_S)\int d\bx_1d\bx^{\prime}_1 \SO{a}(\bx_1)\SO{i}(\bx_1')  \chi_S(\bx_1,\bx_{1'},0^-) =
	-\int d\bx_3 d\bx_4 d\bx_5 d\bx_6\int d\tau_{34}\SO{a}(\bx_3)\SO{i}(\bx_4)
	\\
	\times \qty[\Theta(\tau_{34})e^{i\e{i}{}\tau_{34}}+\Theta(-\tau_{34})e^{i(\e{a}{}-\omega_S)\tau_{34}} ]
	\Bar{T}(\bx_3,\bx_5,\bx_4,\bx_6;\tau_{34})\chi_S(\bx_6,\bx_5;-\tau_{34})e^{i\omega_S\tau_{34}/2}
\end{multline}
(where $\Theta$ is the Heaviside step function) using the fact that
\begin{equation}
	\Theta(\pm\tau)e^{-i\alpha \tau}=\mp\frac{1}{2\pi i}\lim_{\eta\to 0^+}\int d\omega \frac{1}{\omega-\alpha\pm i\eta}e^{-i\omega\tau}
\end{equation}
